Generating Simulated Data

### 2021-03-15 docs/SimData.Rmd
add survey/catch dat csvs for hydra

```{r write-hydra}

@@

>>>>

```{r write-hydra, eval=FALSE}

@@

Survey and catch datasets for hydra from NOBA (same methods as MSSPM). Make this a function that takes output directory name and output names as arguments. 
```{r, eval=FALSE}
o.name <- here("simulated-data/msinput/hydra/")

#multiple surveys named in list object, use as filename
for(s in names(survObsBiom)){
  #arrange into wide format: year, Species1, Species2 ... and write csv
  svbio <- survObsBiom[[s]][[1]] %>%
    #calc_timestep2time(d.name, ., run.prm.file) %>% #this gives an arbitrary start year of 1970
    dplyr::mutate(year = ceiling(time/stepperyr)) %>%
    dplyr::select(species, year, atoutput) %>%
    tidyr::spread(species, atoutput) %>%
    write_csv(paste0(o.name,"observation_biomass_NOBA_",s,".csv"))
}

for(c in names(catchbio_ss)){
  #arrange into wide format: year, Species1, Species2 ... and write csv
  catchbio <- catchbio_ss[[c]][[1]] %>%
    dplyr::mutate(year = time/365) %>%
    dplyr::select(species, year, atoutput) %>%
    tidyr::spread(species, atoutput) %>%
    write_csv(paste0(o.name,"observation_catch_NOBA_",c,".csv"))
}

cat(as.character(meta), file=paste0(here("simulated-data/msinput/hydra/"),"README.txt"))
